\section{Battle for Silver}

Problem summary: given an undirected connected planar graph with weighted vertices, 
find the clique with the maximum value.

Using the knowledge that the graph is planar we can immediately tell that all
possible cliques contain either $n=2$, $n=3$ or $n=4$ vertices. A clique with
$n>4$ will contain $K_5$ and therefore not be planar. In order to find the 
maximum value clique then we must simply search for all possible cliques of 
this size and retain the maximum value seen so far. 

Checking $n=2$ cliques simply requires checking the endpoints of each edge, 
requiring $O(E)$ steps. A simple array of edges was used for this stage. 

To consider all cliques where $n=3$, we take each edge and consider adding 
every vertex in the graph to it. If adding a vertex forms a clique then we 
check its value against the current maximum found. Using an adjacency matrix, 
a vertex addition can be checked for generation of a valid clique in constant 
time requiring $O(VE)$ total steps for these checks.

Finally, in order to consider possible cliques where $n=4$ we generate all
possible pairings of edges where all four endpoints are distinct. With four
distinct vertices we can then verify if they form a clique by checking if
the six required edges are present. Once again, using an adjacency matrix
allows this check to be performed in constant time. 

After checking for all possible cliques we will have retained the maximum
value found, representing the 'chaingroup' with the most silver coins in
its vessels.

Overall this runs in $O(E^2)$ time and $O(V + E)$ memory.
