\section{Jingle Balls}

Problem summary: given a binary Christmas tree with some decorations (balls),
what's the number of balls that needs to be moved to make the tree balanced? We
consider a tree balanced iff it's balanced in terms of balls -- left subtree and
the right subtree must differ in ball count by no more than 1.

Once again, this is a fairly straightforward DP. Since we have at most 1000
nodes, this admits an $O(n^2)$ solution. The recurrence is based on ``how many
balls do I need to move to make substree rooted at $X$ have $B$ balls?''.

Since the ball count can only differ by at most 1, it means subtrees with an
even number of balls have only one way of solving its children ($B/2$ each). For
odd children, we solve both cases (send $B/2$ balls left and $B/2+1$ right, and
the other way as well) and pick the minimum.

Base case is when we are at a leaf (obviously), and a leaf state is admissible
(i.e. leads to a valid solution) iff $0 \leq B \leq 1$. Its cost depends on
whether the leaf has a ball and if the balance is 1. If $B = ball$, then cost is
0 (nothing needs to be moved), and 1 otherwise (we add or remove a ball at this
node).

Note that this ends up double-counting the number of operations required
(additions and removals are counted separately, and they come in pairs). So we
divide the answer by 2.

See code for details, this is really straightforward.\\[5mm]

Oh, this doesn't even need to be DP. I forgot to add caching and it still
passed! \#acmdata \#yolo
